---
title: "pdf_Shucked_weight"
output:
  html_document:
    df_print: paged
---

## Probability Density Estimation

### Packages

```{r}
require(copula)
require(kdensity)
require(VC2copula)
require(VineCopula)
library(cubature)
```

### Data Preparation
```{r}
abalone <- read.csv("abalone.csv")
head(abalone)
```

### Treatment and Outcome
Here we use variable "Length" as the treatment, and "Shucked.weight" as the outcome, and we are aiming to model the probability density function, and we need to use `pobs` functions to get the uniform distribution of the dataset
```{r}
tr <- abalone$Length
ou <- abalone$Shucked.weight
mdata <- cbind(tr, ou)
umdata <- pobs(mdata)
treat <- umdata[,1]
out <- umdata[,2]
```

### Kernel Probability Density Estimation

Here is the estimation of the shucked weight, and comparison with the histogram

```{r}
f <- kdensity(mdata[,2], start = "gaussian", kernel = "gaussian", adjust = 1/3)
hist(mdata[,2], main = "Shucked.weight", xlab = "Shucked.weight", breaks = 100)
par(new=TRUE)
plot(f, xaxt = "n", yaxt = "n", xlab = "", ylab = "", main = "")
```

Here is the estimation of Length
```{r}
g <- kdensity(mdata[,1], start = "gaussian", kernel = "gaussian")
hist(mdata[,1], main = "Length", xlab = "Length")
par(new=TRUE)
plot(g, xaxt = "n", yaxt = "n", xlab = "", ylab = "", main = "")
```


Here is the estimation of stream_first_target_frame_completion_time
```{r}
g <- kdensity(mdata[,1], start = "gamma", kernel = "gamma")
hist(mdata[,1], main = "stream_first_target_frame_completion_time", xlab = "stream_first_target_frame_completion_time")
par(new=TRUE)
plot(g, xaxt = "n", yaxt = "n", xlab = "", ylab = "", main = "")
```

### Copula function estimation

we define marginal functions, just return the function

```{r}
margin_treatment <- function(x){
  return(g(x))
}
margin_out <- function(x){
  return(f(x))
}
```

```{r}
cdt <- function(x){
  res <- integrate(margin_treatment, -Inf, x)$value
  if (res > 1){return(1)}
  else{return(res)}
}
cdo <- function(x){
  res <- integrate(margin_out, -Inf, x)$value
  if (res > 1){return(1)}
  else{return(res)}
}
cdt2vec <- function(t){return(sapply(t, cdt))}
cdo2vec <- function(t){sapply(t, cdo)}
```
We define the conditional probability function, it is a joint distribution

```{r}
mycop <- BiCopEst(out, treat, family = 2)
FOT <- function(o, t){
  a <- cdo2vec(o)
  b <- cdt2vec(t)
  BiCopPDF(a, b, mycop)*margin_out(o)
}

```

when Length is 0.45 and 0.65 respectively

```{r}
FOTm <- function(x){
  FOT(x,0.45)
}
FOTmm <- function(x){
  FOT(x,0.65)
}
FOT1vec <- function(t){sapply(t, FOTm)}
FOT2vec <- function(t){sapply(t, FOTmm)}
```

```{r}
X <- seq(0.01, 1.5, by = 0.05)
E1 <- function(x){
  return(x*FOTm(x))
}
E2 <- function(x){
  return(x*FOTmm(x)) 
}
E1vec <- function(t){return(sapply(t,E1))}
E2vec <- function(t){return(sapply(t,E2))}
```

```{r}
plot(X, FOT1vec(X), ylab = "PDF", xlab = "Shucked.weight", type = "l")
```

```{r}
plot(X, FOT2vec(X), ylab = "PDF", xlab = "Shucked.weight", type = "lr")
```

Then, we can integrate the PDF to get the expectation value under each value of treatment

```{r}
Ex1 <- integrate(E1vec, -Inf, Inf)
Ex2 <- integrate(E2vec, -Inf, Inf)
Ex2$value - Ex1$value
```